Selection coefficients at the phylogenetic and population-genetic scale

### 2022-04-20 manuscript/supp-mat.tex
Updated manuscript with JJ intro and TL experiment description.

@@

    \subsubsection{Proportion of positive selection}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Ssup0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
    \end{minipage}

    \subsubsection{Proportion of negative selection}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Sinf0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
    \end{minipage}

    \subsubsection{Proportion of weak selection}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Seq0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
    \end{minipage}

>>>>

\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\mathrm{fix}}}
\newcommand{\Spop}{\beta}
\newcommand{\SpopMean}{\overline{\Spop}}
\newcommand{\Sphy}{S}
\newcommand{\SphyMean}{\overline{\Sphy}}
\newcommand{\polyDel}{\proba \left[ {\Spop < -1} \right]}
\newcommand{\polyNeutral}{\proba \left[ -1 < \Spop < 1 \right]}
\newcommand{\polyAdv}{\proba \left[ 1 < \Spop  \right]}

@@

    \subsubsection{Proportion of nearly-neutral mutations ($\polyNeutral$)}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Seq0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
    \end{minipage}

    \subsubsection{Proportion of deleterious mutations ($\polyDel$)}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Sinf0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
    \end{minipage}

    \subsubsection{Proportion of advantageous mutations ($\polyAdv$)}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Ssup0.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.32\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
    \end{minipage}
